---
title: "Chapter 8. Visulaizing data distributions"
author: "quartzeese"
date: '2020 3 5 '
output: html_document
---

# Chapter 8 Visualizing data distributions

데이터의 분포를 눈으로 보기 좋다. 

## 8.10 Quantile-quantile plots

First let’s define the theoretical quantiles for the normal distribution. In statistics books we use the symbol  
Φ(x) to define the function that gives us the probability of a standard normal distribution being smaller than  x. So, for example,  
Φ(−1.96)=0.025 and  Φ(1.96)=0.975
 . In R, we can evaluate  Φ using the pnorm function:
 
   
```{r}
library(ggplot2)
library(dslabs)
data(heights)
data(murders)
qnorm(0.975)
#> [1] 1.96 -> z = 1.96일 때 1.96보다 작을 확률이 0.975, 이때 1.96이 quantile 
qnorm(0.975, mean = 5, sd = 2)
#> [1] 8.92

heights %>% filter(sex == "Male") %>%
  ggplot(aes(sample = scale(height))) + 
  geom_qq() +
  geom_abline()

```


## 8.16 ggplot2 geometries

1. barplots

```{r}
murders %>% ggplot(aes(region)) + geom_bar()
```

```{r}

data(murders)
tab <- murders %>% 
  count(region) %>% 
  mutate(proportion = n/sum(n))

tab %>% ggplot(aes(region, proportion)) + geom_bar(stat = "identity")

```

2. Histogram


```{r}
heights %>% 
  filter(sex == "Female") %>% 
  ggplot(aes(height)) + 
  geom_histogram(binwidth = 1)

heights %>% 
  filter(sex == "Female") %>% 
  ggplot(aes(height)) +
  geom_histogram(binwidth = 1, fill = "blue", col = "black") +
  xlab("Male heights in inches") + 
  ggtitle("Histogram")

```


3. Density plots

```{r}
heights %>% 
  filter(sex == "Female") %>%
  ggplot(aes(height)) +
  geom_density()
heights %>% 
  filter(sex == "Female") %>%
  ggplot(aes(height)) +
  geom_density(fill="blue")

heights %>% 
  filter(sex == "Female") %>%
  ggplot(aes(height)) +
  geom_density(fill="blue",adjust=2)

```



4. Boxplots
geom_boxplot

For this geometry, we need arguments x as the categories, and y as the values.

```{r}
heights %>% ggplot(aes(sex,height)) +
  geom_boxplot()

```


5. QQ-plot

```{r}
heights %>% filter(sex=="Male") %>%
  ggplot(aes(sample = height)) +
  geom_qq()
```



```{r}

#standard unit에서 비교
params <- heights %>% filter(sex=="Male") %>%
  summarize(mean = mean(height), sd = sd(height))

heights %>% filter(sex=="Male") %>%
  ggplot(aes(sample = height)) +
  geom_qq(dparams = params) +
  geom_abline()

##처럼ㅎ ㅏ거나 아니면


heights %>% 
  filter(sex=="Male") %>%
  ggplot(aes(sample = scale(height))) + 
  geom_qq() +
  geom_abline()

```


6. Images

ggplot2의 image 만드는 geom은 2가지가 있ㅇ므
geom_tile과 geom_raster 둘이 비슷함. 

```{r}
x <- expand.grid(x = 1:12, y = 1:10) %>% 
  mutate(z = 1:120) 
# tidy version of a matrix, matrix(1:120, 12, 10).
print(x)
```

```{r}
x %>% ggplot(aes(x, y, fill = z)) + 
  geom_raster() + 
  scale_fill_gradientn(colors =  terrain.colors(10))
```


7.qplot


```{r}
x <- heights %>% 
  filter(sex=="Male") %>% 
  pull(height)

qplot(x)
qplot(sample = scale(x)) + geom_abline()

heights %>% qplot(sex, height, data = ., geom = 'boxplot')
qplot(x, bins=15, color = I("black"), xlab = "Population")

#  In general, the function I is used in R to say “keep it as it is”.
# 

```







